---
title: "Data Wrangling Exercise 1"
author: "Laura Rose"
date: "May 22, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step 0: Loading the data into R


```{r message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
refine_original <- read.csv("C:/Users/laura.rose/Documents/refine_original.csv")
```

## Step 1: Cleaning up the company names

```{r}
refine_original$company <- gsub("^[p|f].*", "philips", refine_original$company, ignore.case = TRUE)
refine_original$company <- gsub("^a.*", "akzo", refine_original$company, ignore.case = TRUE)
refine_original$company <- gsub("^v.*", "van houten", refine_original$company, ignore.case = TRUE)
refine_original$company <- gsub("^u.*", "unilever", refine_original$company, ignore.case = TRUE)
```

## Step 2: Separating product code and product number

```{r}
refine_original <- refine_original %>% separate("Product.code...number", c("product_code", "product_number"), sep = "-")
```

## Step 3: Creating a product category variable and replacing the letters with names

```{r}
refine_original <- refine_original %>% mutate(product_cat=product_code)
refine_original$product_cat <- gsub("p", "Smartphone", refine_original$product_cat)
refine_original$product_cat <- gsub("v", "TV", refine_original$product_cat)
refine_original$product_cat <- gsub("x", "Laptop", refine_original$product_cat)
refine_original$product_cat <- gsub("q", "Tablet", refine_original$product_cat)
```

## Step 4: Creating the full address column

```{r}
refine_original <- unite(refine_original, full_address, address:country, sep = ",", remove = FALSE)
```

## Step 5: Creating new dummy variables and setting the new binary columns equal to the dummary variables
```{r}
dummy_philips <- as.numeric(refine_original$company == "philips")
dummy_akzo <- as.numeric(refine_original$company == "akzo")
dummy_van_houten <- as.numeric(refine_original$company == "van houten")
dummy_unilever <- as.numeric(refine_original$company == "unilever")

dummy_smartphone <- as.numeric(refine_original$product_cat == "Smartphone")
dummy_tv <- as.numeric(refine_original$product_cat == "TV")
dummy_laptop <- as.numeric(refine_original$product_cat == "Laptop")
dummy_tablet <- as.numeric(refine_original$product_cat == "Tablet")
refine_original <- mutate(refine_original, company_philips = dummy_philips, company_akzo = dummy_akzo, company_van_houten = dummy_van_houten, company_unilever = dummy_unilever, product_smartphone = dummy_smartphone, product_TV = dummy_tv, product_laptop = dummy_laptop, product_tablet = dummy_tablet)
```

## Step 6: Writing the cleaned-up data frame to a new CSV
```{r}
write.csv(refine_original, file = "refine_clean.csv")
```
